Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Regen
Add anchor and its reference as example

```{r preprocessing}
collapse_ages <- function(data,ages=c('15-49','50-69'),age_lab='age_cat'){
  target_min_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][1]))
  target_max_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][2]))
  min_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][1]))
  max_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][2]))
  genders <- unique(data$sex)
  if(ncol(data)>3) {
    reformatted <- do.call(rbind,lapply(1:length(ages),
    function(x) t(sapply(genders,
          function(y) 
            if(ncol(data)>3) colSums(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
          else sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         ))
  ))
  data.frame(age_cat=rep(ages,each=2),sex=rep(genders,2),reformatted,stringsAsFactors=F)
  }else{
  reformatted <- do.call(c,lapply(1:length(ages),
    function(x) sapply(genders,
          function(y) 
            sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         )
  ))
  data.frame(age=rep(ages,each=2),sex=rep(genders,2),population=as.numeric(reformatted),stringsAsFactors=F)
  }
}

@@

Change in YLL per 100,000 people by scenario

>>>>

Click here: [change in yll](#change_in_yll_100k)

```{r preprocessing}

collapse_ages <- function(data,ages=c('15-49','50-69'),age_lab='age_cat'){
  target_min_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][1]))
  target_max_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][2]))
  min_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][1]))
  max_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][2]))
  genders <- unique(data$sex)
  if(ncol(data)>3) {
    reformatted <- do.call(rbind,lapply(1:length(ages),
    function(x) t(sapply(genders,
          function(y) 
            if(ncol(data)>3) colSums(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
          else sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         ))
  ))
  data.frame(age_cat=rep(ages,each=2),sex=rep(genders,2),reformatted,stringsAsFactors=F)
  }else{
  reformatted <- do.call(c,lapply(1:length(ages),
    function(x) sapply(genders,
          function(y) 
            sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         )
  ))
  data.frame(age=rep(ages,each=2),sex=rep(genders,2),population=as.numeric(reformatted),stringsAsFactors=F)
  }
}

@@

## Change in YLL due to disease per 100,000 {#change_in_yll_100k}
